Correcting K-correction: dark energy is based on a math error from 1930

### 2025-02-04 paper/dark_energy_corrections.tex
Move references into main tex file

\bibliography{references}

>>>>

\begin{filecontents}{references.bib}
@article{riess1998,
  title={Observational evidence from supernovae for an accelerating universe and a cosmological constant},
  author={Riess, Adam G and Filippenko, Alexei V and Challis, Peter and Clocchiatti, Alejandro and Diercks, Alan and Garnavich, Peter M and Gilliland, Ron L and Hogan, Craig J and Jha, Saurabh and Kirshner, Robert P and others},
  journal={The astronomical journal},
  volume={116},
  number={3},
  pages={1009},
  year={1998},
  publisher={IOP Publishing}
}

@article{perlmutter1999,
  title={Measurements of $\Omega$ and $\Lambda$ from 42 high-redshift supernovae},
  author={Perlmutter, Saul and Aldering, Goldhaber and Goldhaber, Gerson and Knop, Richard A and Nugent, Peter and Castro, Patricia G and Deustua, Susana and Fabbro, Sebastien and Goobar, Ariel and Groom, Donald E and others},
  journal={The Astrophysical Journal},
  volume={517},
  number={2},
  pages={565},
  year={1999},
  publisher={IOP Publishing}
}

@article{perlmutter2003,
  title={Measuring cosmology with supernovae},
  author={Perlmutter, Saul and Schmidt, Brian P},
  journal={Supernovae and Gamma-Ray Bursters},
  pages={195--217},
  year={2003},
  publisher={Springer}
}

@book{weinberg2008,
  title={Cosmology},
  author={Weinberg, Steven},
  year={2008},
  publisher={OUP Oxford}
}

@article{straumann2012,
  title={The 2011 Nobel Prize in Physics},
  author={Straumann, Norbert and Z{\"u}rich, Uni},
  journal={SPG Mitteilungen},
  number={36},
  year={2012}
}

@article{betoule2014,
  title={Improved cosmological constraints from a joint analysis of the SDSS-II and SNLS supernova samples},
  author={Betoule, MEA and Kessler, R and Guy, J and Mosher, J and Hardin, D and Biswas, R and Astier, P and El-Hage, P and Konig, M and Kuhlmann, S and others},
  journal={Astronomy \& Astrophysics},
  volume={568},
  pages={A22},
  year={2014},
  publisher={EDP Sciences}
}

@article{siegel1982,
  title={Robust regression using repeated medians},
  author={Siegel, Andrew F},
  journal={Biometrika},
  volume={69},
  number={1},
  pages={242--244},
  year={1982},
  publisher={Oxford University Press}
}

@article{verde2019,
  title={Tensions between the early and late Universe},
  author={Verde, Licia and Treu, Tommaso and Riess, Adam G},
  journal={Nature Astronomy},
  volume={3},
  number={10},
  pages={891--895},
  year={2019},
  publisher={Nature Publishing Group UK London}
}

@article{abbott2024,
  title={The Dark Energy Survey: Cosmology Results With $\sim$1500 New High-redshift Type Ia Supernovae Using The Full 5-year Dataset},
  author={DES-Collaboration and Abbott, TMC and Acevedo, M and Aguena, M and Alarcon, A and Allam, S and Alves, O and Amon, A and Andrade-Oliveira, F and Annis, J and Armstrong, P and others},
  journal={arXiv preprint arXiv:2401.02929},
  year={2024}
}

@article{perivolaropoulos2022,
  title={Challenges for $\Lambda$CDM: An update},
  author={Perivolaropoulos, Leandros and Skara, Foteini},
  journal={New Astronomy Reviews},
  volume={95},
  pages={101659},
  year={2022},
  publisher={Elsevier}
}

@article{flaugher2015,
  title={The dark energy camera},
  author={Flaugher, Brenna and Diehl, HT and Honscheid, K and Abbott, TMC and Alvarez, O and Angstadt, R and Annis, JT and Antonik, M and Ballester, O and Beaufore, L and others},
  journal={The Astronomical Journal},
  volume={150},
  number={5},
  pages={150},
  year={2015},
  publisher={IOP Publishing}
}

@article{vincenzi2024,
  title={The Dark Energy Survey Supernova Program: Cosmological Analysis and Systematic Uncertainties},
  author={Vincenzi, M and Brout, D and Armstrong, P and Popovic, B and Taylor, G and Acevedo, M and Camilleri, R and Chen, R and Davis, TM and Lee, J and others},
  journal={The Astrophysical Journal},
  volume={975},
  number={1},
  pages={86},
  year={2024},
  publisher={IOP Publishing}
}

@article{shao2013,
  title={The energy loss of photons and cosmological redshift},
  author={Shao, Ming-Hui},
  journal={Physics Essays},
  volume={26},
  number={2},
  pages={183--190},
  year={2013},
  publisher={Physics Essays Publication}
}

@article{white2024,
  title={The Dark Energy Survey Supernova Program: Slow supernovae show cosmological time dilation out to $ z \sim 1$},
  author={White, Ryan MT and Davis, Tamara M and Lewis, Geraint F and Lidman, Christopher and Shah, Paul and Abbott, TMC and Aguena, M and Allam, S and Andrade-Oliveira, F and Asorey, J and others},
  journal={arXiv preprint arXiv:2406.05050},
  year={2024}
}

@article{blondin2008,
  title={Time dilation in type Ia supernova spectra at high redshift},
  author={Blondin, Stephanie and Davis, Tamara M and Krisciunas, Kevin and Schmidt, Brian P and Sollerman, J and Wood-Vasey, WM and Becker, AC and Challis, P and Clocchiatti, A and Damke, G and others},
  journal={The Astrophysical Journal},
  volume={682},
  number={2},
  pages={724},
  year={2008},
  publisher={IOP Publishing}
}

@article{zwicky1929,
  title={On the redshift of spectral lines through interstellar space},
  author={Zwicky, Fritz},
  journal={Proceedings of the National Academy of Sciences},
  volume={15},
  number={10},
  pages={773--779},
  year={1929},
  publisher={National Acad Sciences}
}

@article{tolman1930,
  title={On the estimation of distances in a curved universe with a non-static line element},
  author={Tolman, Richard C},
  journal={Proceedings of the National Academy of Sciences},
  volume={16},
  number={7},
  pages={511--520},
  year={1930},
  publisher={National Acad Sciences}
}

@article{desitter1934,
  title={On distance, magnitude, and related quantities in an expanding universe},
  author={de Sitter, Willem},
  journal={Bulletin of the Astronomical Institutes of the Netherlands, Vol. 7, p. 205},
  volume={7},
  pages={205},
  year={1934}
}

@article{hubble1935,
  title={Two methods of investigating the nature of the nebular redshift},
  author={Hubble, Edwin and Tolman, Richard C},
  journal={Astrophysical Journal, vol. 82, p. 302},
  volume={82},
  pages={302},
  year={1935}
}

@article{oke1968,
  title={Energy distributions, k corrections, and the Stebbins-Whitford effect for giant elliptical galaxies},
  author={Oke, John Beverley and Sandage, Allan},
  journal={Astrophysical Journal, vol. 154, p. 21},
  volume={154},
  pages={21},
  year={1968}
}

@article{kim1996,
  title={A generalized K correction for type Ia supernovae: comparing R-band photometry beyond z= 0.2 with B, V, and R-band nearby photometry},
  author={Kim, Alex and Goobar, Ariel and Perlmutter, Saul},
  journal={Publications of the Astronomical Society of the Pacific},
  volume={108},
  number={720},
  pages={190},
  year={1996},
  publisher={IOP Publishing}
}

@article{hsiao2007,
  title={K-corrections and spectral templates of Type Ia supernovae},
  author={Hsiao, Eric Y and Conley, A and Howell, DA and Sullivan, M and Pritchet, CJ and Carlberg, RG and Nugent, PE and Phillips, MM},
  journal={The Astrophysical Journal},
  volume={663},
  number={2},
  pages={1187},
  year={2007},
  publisher={IOP Publishing}
}

@article{kessler2009,
  title={SNANA: A public software package for supernova analysis},
  author={Kessler, Richard and Bernstein, Joseph P and Cinabro, David and Dilday, Benjamin and Frieman, Joshua A and Jha, Saurabh and Kuhlmann, Stephen and Miknaitis, Gajus and Sako, Masao and Taylor, Matt and others},
  journal={Publications of the Astronomical Society of the Pacific},
  volume={121},
  number={883},
  pages={1028},
  year={2009},
  publisher={IOP Publishing}
}

@article{burns2010,
  title={The Carnegie supernova project: light-curve fitting with SNooPy},
  author={Burns, Christopher R and Stritzinger, Maximilian and Phillips, MM and Kattner, ShiAnne and Persson, SE and Madore, Barry F and Freedman, Wendy L and Boldt, Luis and Campillay, Abdo and Contreras, Carlos and others},
  journal={The Astronomical Journal},
  volume={141},
  number={1},
  pages={19},
  year={2010},
  publisher={IOP Publishing}
}

@article{planck2015,
  title={Planck 2015 results-xiii. cosmological parameters},
  author={Planck-Collaboration and Ade, Peter AR and Aghanim, Nabila and Arnaud, M and Ashdown, Mark and Aumont, Jea and Baccigalupi, Carlo and Banday, AJ and Barreiro, RB and Bartlett, JG and Bartolo, Nicola and others},
  journal={Astronomy \& Astrophysics},
  volume={594},
  pages={A13},
  year={2016},
  publisher={EDP sciences}
}

@article{planck2020,
  title={Planck 2018 results-VI. Cosmological parameters},
  author={Planck-Collaboration and Aghanim, Nabila and Akrami, Yashar and Ashdown, Mark and Aumont, Jonathan and Baccigalupi, Carlo and Ballardini, Mario and Banday, Anthony J and Barreiro, RB and Bartolo, Nicola and Basak, S and others},
  journal={Astronomy \& Astrophysics},
  volume={641},
  pages={A6},
  year={2020},
  publisher={EDP sciences}
}

@article{camarena2020,
  title={Local determination of the Hubble constant and the deceleration parameter},
  author={Camarena, David and Marra, Valerio},
  journal={Physical Review Research},
  volume={2},
  number={1},
  pages={013028},
  year={2020},
  publisher={APS}
}

@book{peebles2020,
  title={Cosmology’s century: An inside history of our modern understanding of the universe},
  author={Peebles, Phillip James Edwin},
  year={2020},
  publisher={Princeton University Press}
}

@article{lesser2015,
  title={A summary of charge-coupled devices for astronomy},
  author={Lesser, Michael},
  journal={Publications of the Astronomical Society of the Pacific},
  volume={127},
  number={957},
  pages={1097--1104},
  year={2015},
  publisher={The Astronomical Society of the Pacific}
}
\end{filecontents}
\bibliography{references}
